MinCall --- MinION end2end deep learning basecaller

### 2017-06-30 paper/main.tex

@@

>>>>

In appendix~\ref{app:evaluation:CIGAR} the histogram figure~\ref{fg:cigar_op_dist} shows how matches, mismatches, insertions, and deletions are distributed across the reads. It is shown that mismatches and insertion occur more frequently at the beginnings and the ends of the reads. This is not only the case for the developed basecaller, but all other show the same property. This could be due to lack of context information from both sides when edges are base called.

@@

\begin{figure}[!ht]
	\begin{center}
		\includegraphics[width=1\textwidth]{./imgs/operation_distributed_r9.png}
		\caption{Histogram of alignment operations over relative position inside of read}
		\label{fg:cigar_op_dist}
	\end{center}
\end{figure}
